R Notebook

### 2017-07-06 doc/RMD/wmn-differentiation.Rmd
change DAPC to host/region

```{r dapc, fig.width = 5, fig.height = 5.5}
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = FALSE,
        col = viridis::plasma(3), 
        bg.inset = "grey90",
        bg = "grey90")

ggcompoplot::ggcompoplot(bebug_dapc, bebug, pal = viridis::plasma(3)) +
  theme(legend.position = "top")
```

>>>>

```{r dapc, fig.width = 5, fig.height = 5.5}
setPop(bebug) <- ~Host/Region
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, #clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = FALSE,
        # col = viridis::plasma(3), 
        bg.inset = "grey90",
        bg = "grey90")

ggcompoplot::ggcompoplot(bebug_dapc, bebug) + #, pal = viridis::plasma(3)) +
  theme(legend.position = "top")
```
